---
title: "List Columns and Bootstrapping"
author: "Jeff Goldsmith"
date: "11/15/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rnoaa)
```


## Weather data

```{r, cache = TRUE}
weather = 
  meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2016-01-01",
                      date_max = "2016-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
weather_nest = 
  weather %>% 
  nest(date:tmin)
```

```{r}
weather_nest

weather_nest$data
```

```{r}
weather_nest$data[[1]]

lm(tmax ~ tmin, data = weather_nest$data[[3]])

```

### Operations on list columns

```{r}
lm(tmax ~ tmin, data = weather_nest$data[[1]])
lm(tmax ~ tmin, data = weather_nest$data[[2]])
lm(tmax ~ tmin, data = weather_nest$data[[3]])
```


write a function to fit tmax vs tmin for a given dataframe.

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}
```

make sure this works ...

```{r}
weather_lm(weather_nest$data[[1]]) %>% broom::tidy()
weather_lm(weather_nest$data[[2]])
weather_lm(weather_nest$data[[3]])
```


can we loop or use a loop function ...

YES

```{r}
map(weather_nest$data, weather_lm)
```

Fit some models, and tidy the output
```{r}
weather_nest %>% 
  mutate(models = map(data, weather_lm),
         results = map(models, broom::tidy))
```

Add an unnest step to see results

```{r}
weather_nest %>% 
  mutate(models = map(data, weather_lm),
         results = map(models, broom::tidy)) %>% 
  select(-data, -models) %>% 
  unnest()
```







### instacart data

```{r}
instacart = read_csv("./data/instacart_train_data.csv.zip")

instacart_nest = instacart %>% 
  group_by(department) %>% 
  nest() %>% 
  filter(department %in% c("deli", "produce", "snacks", "beverages"))

instacart_nest
```


let's try to summarize `order_hour_of_day`

```{r}
summary(instacart_nest$data[[1]]$order_hour_of_day)
```

do this using map

```{r}
instacart_nest %>% 
  mutate(summary = map(data, ~summary(.x[["order_hour_of_day"]])),
         results = map(summary, broom::tidy)) %>% 
  select(-data, -summary) %>% 
  unnest()
```


### Bootstrapping

```{r}
set.seed(10)

n_samp = 250

sim_df_const = tibble(
  x = rnorm(n_samp, 1, 1),
  error = rnorm(n_samp, 0, 1),
  y = 2 + 3 * x + error
)

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)

bind_rows(
  mutate(sim_df_const, data = "sim_df_const"),
  mutate(sim_df_nonconst, data = "sim_df_nonconst")
) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data) 
```


lets fit the models

```{r}
lm(y ~ x, data = sim_df_const) %>% summary()
lm(y ~ x, data = sim_df_nonconst) %>% summary()
```


### Draw a sample

```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}

boot_sample(sim_df_nonconst)

```



### Draw lots of samples ...

```{r}
boot_straps = data_frame(
  strap_number = 1:1000,
  strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
)

boot_straps
```



### Analysis of bootstrap samples

```{r}
boot_results =
  boot_straps %>% 
  mutate(models = map(strap_sample, ~lm(y ~ x, data = .x)),
         results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest()
```


Check inference ...

```{r}

boot_results %>% 
  group_by(term) %>% 
  summarize(se = sd(estimate))

lm(y ~ x, data = sim_df_nonconst) %>% broom::tidy()


```


### `bootstrap`

```{r}
library(modelr)

boot_results = 
  sim_df_const %>% 
  bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x)),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest()

boot_results %>% 
  group_by(term) %>% 
  summarize(se = sd(estimate))
```








