---
title: "Writing Functions"
author: "Jeff Goldsmith"
date: "11/8/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Simple function

```{r}
set.seed(1)

x = rnorm(25)

mean(x) / sd(x)
```

Let's see this as a function...

```{r}
z_score = function(x) {
  
  z = mean(x) / sd(x)
  
  z
  
}

z_score(x)
```

Unintended argument values ...

```{r, error = TRUE}
z_score(19.375)
z_score("my name is jeff")
z_score(iris)
z_score(c(TRUE, TRUE, FALSE, TRUE))
```

Add some control statements.

```{r}
z_score = function(x) {
  
  if (!is.numeric(x)) {
    stop("x must be numeric")
  } else if (length(x) < 3) {
    stop("x must have three or more entries")
  }
  
  z = mean(x) / sd(x)
  
  z
  
}
```

## Multiple outputs

Add mean and sd to output ...


```{r}
z_score = function(x) {
  
  if (!is.numeric(x)) {
    stop("x must be numeric")
  } else if (length(x) < 3) {
    stop("x must have three or more entries")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  z = mean_x / sd_x
  
  data_frame(mean = mean_x,
             sd = sd_x,
             z = z)
  
}

z_score(x)
```


### A bit more interesting ...

Starting code.

```{r}
sim_data = tibble(
  x = runif(30),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

ggplot(sim_data, aes(x = x, y = y)) + geom_point()

ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]
```

Let's write a function to simulate SLR and produce estimates ...

```{r}
sim_regression = function(n, beta0, beta1) {
  
  sim_data = tibble(
    x = runif(n),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )

  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
  
}
```

### LoTR function!!

Repeating code 3x was a real burden when we were reading in the LoTR data -- but now we can write a function to do it!

First thing to do is identify the inputs. In this case, what changes across code chunks is the cell range and movie title. I'll also include the path to the spreadsheet as an argument, in case I need to access it from somewhere else.

Give those inputs, the body of my function is, essentially, the code I already wrote -- I'll copy that in.

Lastly, I need to define my output. The code I have produces a dataframe, and that's a pretty okay output format.  

The function to abstract this process is below.

```{r}
library(readxl)
library(janitor)

lotr_word_reader = function(path = "./data/LotR_Words.xlsx", cell_range, movie_name) {
  
  df = read_excel(path, range = cell_range) %>%
    clean_names() %>%
    gather(key = sex, value = words, female:male) %>%
    mutate(race = tolower(race),
           movie = movie_name)
  
  df
  
}

bind_rows(
  lotr_word_reader(cell_range = "B3:D6", movie_name = "Fellowship"),
  lotr_word_reader(cell_range = "F3:H6", movie_name = "Two Towers"),
  lotr_word_reader(cell_range = "J3:L6", movie_name = "Return")
)

```


